\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-1pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}



\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Daniel Truong} \\ \vspace{1pt}
    \href{https://linkedin.com/in/dantruong52435}{\underline{linkedin.com/in/dantruong52435}} $|$
    \href{https://github.com/dantruong}{\underline{github.com/dantruong}}
\end{center}

%-----------Summary-----------------
\section{Professional Summary}
Detail-oriented programmer with 10+ years in higher education IT, experienced in software development, data visualization, and systems integration. Proficient in Java, Python, SQL, and R with a strong focus on delivering scalable technical solutions.

%-----------EDUCATION-----------------
\section{Education}
  	\resumeSubHeadingListStart
		\resumeSubheading
			{State University of New York (SUNY) Polytechnic Institute}{Utica, NY}
			{Master of Science in Information Design and Technology}{Jan. 2015 -- May 2021}
			\item
			\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
				\textbf{State University of New York at Oswego} & Oswego, NY \\
			\end{tabular*}\vspace{-0pt}
			\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
				\textit{\small Master of Science in Biomedical and Health Informatics} & \textit{\small Aug. 2017 -- Dec. 2019} \\
				\textit{\small Bachelor of Science in Applied Mathematical Economics} & \textit{\small Aug. 2009 -- May 2014} \\
			\end{tabular*}\vspace{-0pt}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  	\resumeSubHeadingListStart
    	\resumeSubheading
      		{State University of New York at Oswego}{Oswego, NY}
      		{Campus Technology Services}{May 2014 - Present}
      		\resumeItemListStart
				\resumeItem{Programmer/Analyst (Jun. 2022 - Present)}{}
				\begin{itemize}
					\item Design and maintain dynamic reporting dashboards in Evisions Argos, using complex Oracle SQL queries to support administrative decision-making.
					\item Develop data pipelines and integrations between Banner and third-party systems (e.g., Medicat, HelioCampus AC) using PL/SQL, Unix shell scripting, and secure SFTP.
					\item Led the migration of historical IT ticketing data from ServiceNow to TeamDynamix using R and REST APIs. Currently TeamDynamix co-administrator.
					\item Support university-wide data initiatives by scripting automated ETL processes and ensuring data quality across platforms.
				\end{itemize}
				\resumeItem{Technology Support Professional (Jun. 2018 - Jun. 2022)}{}
				\begin{itemize}
					\item Provided IT support and infrastructure management for faculty, staff, and classrooms, including endpoint deployment via SCCM and scripting automation using PowerShell.
					\item Advised on procurement strategies and supported grant-based educational technology initiatives.
				\end{itemize}
				\resumeItem{Desktop Support Technician (May 2014 - Jun. 2018)}{}
				\begin{itemize}
					\item Delivered hardware, software, and network support across campus, including hands-on Dell/Apple endpoint and HP printing hardware repairs and remote troubleshooting with BeyondTrust.
					\item Managed desktop imaging, printer configurations, and Active Directory maintenance for university endpoints.
				\end{itemize}
      		\resumeItemListEnd
	\resumeSubHeadingListEnd
	
%-----------PROJECTS-----------------
\section{Projects}
  	\resumeSubHeadingListStart
	  	\resumeSubItem{TeamDynamix Integration}{Led the migration from ServiceNow, using R scripts to automate ticket and asset import via API, streamlining IT operations (\textit{R, REST API, JSON}).}
   		\resumeSubItem{NYS-Influenza-Map}{Created an interactive dashboard to visualize flu cases by county in NYS, enabling clearer trend insights for public health analysis(\textit{R, Shiny, ggplot2}).}
   		\resumeSubItem{jayDungeon}{Dungeon-crawling text adventure game (\textit{Java, XML, Object-oriented Design}).}
    	\resumeSubItem{The High Screen}{Sports and Entertainment blog, powered by Jekyll (\textit{HTML5, CSS, JavaScript, Bootstrap, Markdown}).}
  	\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Programming Skills}
  	\resumeSubHeadingListStart
		\resumeSubItem{Languages}{Python, Java, SQL (MySQL, PL/SQL), R, PHP, JavaScript}
		\resumeSubItem{Frameworks/Libraries}{Shiny, Bootstrap, Jekyll, ggplot2} 
		\resumeSubItem{Tools}{GitHub, Postman, VS Code, Jupyter, RStudio, NetBeans} 
		\resumeSubItem{IT Systems}{Windows Server, Active Directory, Hyper-V, VMWare, Microsoft SCCM/MECM, ServiceNow, TeamDynamix} 
	\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}